---
title: "Oliver Wyman Expert Search Models"
author: "Aria Muchhal"
date: '2023-04-16'
output: pdf_document
---

## Set Up

```{r echo=T, results='hide'}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.align = "center",
	message = FALSE,
	warning = FALSE,
	collapse = TRUE
)
```

## Load Packages into R

```{r echo=T, results='hide'}
library(knitr)
library(tinytex)
library(latexpdf)
library(magrittr)
library(readxl)
library(writexl)
library(tidyr)
library(purrr)
library(lmtest)
library(sandwich)
library(fixest)
library(modelsummary)
library(lattice)
library(AER)
library(cellranger)
library(dplyr)
library(ggplot2)
library(lubridate)
```

## Expert Search Models

```{r echo=T, results='hide'}
A=1.5
B=2
C=0
D=1
E=5
F=.5
G=8
H=6
I=1
J=.5
K=15
DD=1
ED=5
FD=.1
GD=6
HD=4
```

## Add Functions

```{r echo=T, results='hide'}
teamsize<-function(a) {
print(1-((1+C)/(1+A^(B-a))))
}

timelapse<-function(a){
  print(2^(-a/K))
}

authors<-function(a){
  print(1-(1-C)/(1+A^(B-(a))))
}

docnum<-function(a){
  print(1-1/(a))
}

```

## Now, import your dataframe into R: Import-\> From Excel\_ -\> Browse(find file) -\> sheet(whichever you'd like, but eventually import all), 

## Skip=1, first row as names. 

## Make sure to label different sheets differently.

### It will be better for you to repeat all these steps with each dataframe. You could set up a for loop for this once you're sure you've copied everything down and your software is running properly for 1 iteration--this is a heavy process for your computer, so you don't want to overload it because of one misplaced parenthetical.

```{r echo=T, results='hide'}
library(readxl)
Expert_Search_Models_1_ <- read_excel("C:/Users/muchh/OneDrive/Documents/R/Oliver Wyman/Expert Search Models (1).xlsx", 
    sheet = "Person 1", skip = 1)
Expert_Search_Models_2_ <- read_excel("C:/Users/muchh/OneDrive/Documents/R/Oliver Wyman/Expert Search Models (1).xlsx", 
    sheet = "Person 2", skip = 1)
Expert_Search_Models_3_ <- read_excel("C:/Users/muchh/OneDrive/Documents/R/Oliver Wyman/Expert Search Models (1).xlsx", 
    sheet = "Person 3", skip = 1)
Expert_Search_Models_4_ <- read_excel("C:/Users/muchh/OneDrive/Documents/R/Oliver Wyman/Expert Search Models (1).xlsx", 
sheet = "Person 4", range = "A2:S12")
```


## Aggregate your dataframe

```{r echo=T, results='hide'}
Hours<-Expert_Search_Models_1_ %>% select(starts_with("Hours"))
Teams<-Expert_Search_Models_1_ %>% select(ends_with("Size"))

```

## Run Calculations

```{r echo=T, results='hide'}
TeamSize1<-as.data.frame(apply(Teams,c(1, 2), FUN=teamsize))
Timelapse1<-as.data.frame(timelapse(Expert_Search_Models_1_$TimeLapse))
Authors1<-as.data.frame(authors(Expert_Search_Models_1_$Authors))
DocsNum1<-as.data.frame(docnum(Expert_Search_Models_1_$Docs))

ProjScore1 <- vector("numeric", length = ncol(TeamSize1))
for(i in 1:ncol(TeamSize1)){
  ProjScore1[i] <- as.data.frame(TeamSize1[ ,i]+Timelapse1)
}
ProjScore1<-as.data.frame(ProjScore1)
DocScore1<-DocsNum1+Authors1+Timelapse1

ExpertScore1 <- vector("numeric", length = 6)
for(i in 1:6) {
  ExpertScore1[i] <- as.data.frame(ProjScore1[[i]]+DocScore1)
}
ExpertScore1<-as.data.frame(ExpertScore1)

```

## Export your data
```{r echo=T, results='hide'}
write_xlsx(ProjScore1, "C:/Users/muchh/OneDrive/Documents/R/Oliver Wyman/ProjPerson_1_Final.xlsx")
write_xlsx(DocScore1, "C:/Users/muchh/OneDrive/Documents/R/Oliver Wyman/DocPerson_1_Final.xlsx")
write_xlsx(ExpertScore1, "C:/Users/muchh/OneDrive/Documents/R/Oliver Wyman/ExpertPerson_1_Final.xlsx")
```

## Repeat!
```{r echo=T, results='hide'}
Hours3<-Expert_Search_Models_3_ %>% select(starts_with("Hours"))
Teams3<-Expert_Search_Models_3_ %>% select(ends_with("Size"))
TeamSize3<-as.data.frame(apply(Teams3,c(1, 2), FUN=teamsize))
Timelapse3<-as.data.frame(timelapse(Expert_Search_Models_3_$TimeLapse))
Authors3<-as.data.frame(authors(Expert_Search_Models_3_$Authors))
DocsNum3<-as.data.frame(docnum(Expert_Search_Models_3_$Docs))

ProjScore3 <- vector("numeric", length = ncol(TeamSize3))
for(i in 1:ncol(TeamSize3)){
  ProjScore3[i] <- as.data.frame(TeamSize3[ ,i]+Timelapse3)
}
ProjScore3<-as.data.frame(ProjScore3)
DocScore3<-DocsNum3+Authors3+Timelapse3

ExpertScore3 <- vector("numeric", length = 6)
for(i in 1:6) {
  ExpertScore3[i] <- as.data.frame(ProjScore3[[i]]+DocScore3)
}
ExpertScore3<-as.data.frame(ExpertScore3)

write_xlsx(ProjScore3, "C:/Users/muchh/OneDrive/Documents/R/Oliver Wyman/ProjPerson_3_Final.xlsx")
write_xlsx(DocScore3, "C:/Users/muchh/OneDrive/Documents/R/Oliver Wyman/DocPerson_3_Final.xlsx")
write_xlsx(ExpertScore3, "C:/Users/muchh/OneDrive/Documents/R/Oliver Wyman/ExpertPerson_3_Final.xlsx")
```

```{r echo=T, results='hide'}
Hours4<-Expert_Search_Models_4_ %>% select(starts_with("Hours"))
Teams4<-Expert_Search_Models_4_ %>% select(ends_with("Size"))
TeamSize4<-as.data.frame(apply(Teams4,c(1, 2), FUN=teamsize))
Timelapse4<-as.data.frame(timelapse(Expert_Search_Models_4_$TimeLapse))
Authors4<-as.data.frame(authors(Expert_Search_Models_4_$Authors))
DocsNum4<-as.data.frame(docnum(Expert_Search_Models_4_$Docs))

ProjScore4 <- vector("numeric", length = ncol(TeamSize4))
for(i in 1:ncol(TeamSize4)){
  ProjScore4[i] <- as.data.frame(TeamSize4[ ,i]+Timelapse4)
}
ProjScore4<-as.data.frame(ProjScore4)
DocScore4<-DocsNum4+Authors4+Timelapse4

ExpertScore4 <- vector("numeric", length = 6)
for(i in 1:6) {
  ExpertScore4[i] <- as.data.frame(ProjScore4[[i]]+DocScore4)
}
ExpertScore4<-as.data.frame(ExpertScore4)

write_xlsx(ProjScore4, "C:/Users/muchh/OneDrive/Documents/R/Oliver Wyman/ProjPerson_4_Final.xlsx")
write_xlsx(DocScore4, "C:/Users/muchh/OneDrive/Documents/R/Oliver Wyman/DocPerson_4_Final.xlsx")
write_xlsx(ExpertScore4, "C:/Users/muchh/OneDrive/Documents/R/Oliver Wyman/ExpertPerson_4_Final.xlsx")
```

